\hfill ~\\[-30mm] \phantom{h} \hfill\mbox{\small pre-print number if any?} \\[1cm] \vspace{13mm} \textbf{Precise predictions for same sign W-bosons scattering at the LHC}

### 2017-12-08 Draft/abstract.tex
First attempt of Mathieu on draft, to be continued

\begin{abstract}
\noindent
Abstract to be written here.
\end{abstract}
\thispagestyle{empty}
\vfill
\newpage
\setcounter{page}{1}

>>>>

\begin{abstract}
\noindent

In this article, a detailed study of the vector-boson scattering of two positively charged W bosons is presented.
In particular, a comparison between the full NLO QCD corrections against several approximations is carried out.
This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
This allows to infer precisely the quality of such approximations.
Finally, NLO predictions matched to various parton shower are discussed.
This study allows thus to infer the systematics related to vector-boson scattering at the NLO-QCD level and beyond.

\end{abstract}
\thispagestyle{empty}
\vfill
\newpage
\setcounter{page}{1}

### 2017-12-08 Draft/article.tex
Update article.tex
First attempt of Mathieu on draft, to be continued

\date{}
\author{
Simon Brass$^{1\,}$,
Ansgar Denner$^{2\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4,5\,}$, \\
Alexander Karlberg$^{6\,}$, 
Mathieu Pellen$^{2\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{7\,}$,
Michael Rauch$^{8\,}$,
J\"urgen Reuter$^{9\,}$, \\
Vincent Rothe$^{9\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{9\,}$,
Marco Zaro$^{10\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
{\small\it Via A. Bassi 6, \linebreak %
        27100 Pavia, %
        Italy}\\[3mm]
%        
{\small\it
$^{5}$IBM Italia s.p.a.} \\ %
{\small\it Circonvallazione Idroscalo , \linebreak %
        20090 Segrate (MI), %
        Italy}\\[3mm]
        %
{\small\it
$^6$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
$^7${\small\it
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
{\small\it Via P. Giuria 1, \linebreak %
        10125 Torino, %
        Italy}\\[3mm]
        %
{\small\it
$^8$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^9$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^{10}$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]        
        }

@@

\section{Definition of the process}

\section{Details of the calculations}

@@

\section{Fixed order comparisons}

\subsection{Cross sections}

\input{crosssection}

\subsection{Differential distributions}

\input{distributions}

\section{Influence of the fiducial region}

\section{Matching to parton shower}

@@

\section{Conclusion}

>>>>

\date{}
\author{
Benedikt Biedermann$^{1\,}$,
Simon Brass$^{2\,}$,
Ansgar Denner$^{1\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4,5\,}$, \\
Alexander Karlberg$^{6\,}$, 
Mathieu Pellen$^{1\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{7\,}$,
Michael Rauch$^{8\,}$,
J\"urgen Reuter$^{9\,}$, \\
Vincent Rothe$^{9\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{9\,}$,
Marco Zaro$^{10\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
{\small\it Via A. Bassi 6, \linebreak %
        27100 Pavia, %
        Italy}\\[3mm]
%        
{\small\it
$^{5}$IBM Italia s.p.a.} \\ %
{\small\it Circonvallazione Idroscalo , \linebreak %
        20090 Segrate (MI), %
        Italy}\\[3mm]
        %
{\small\it
$^6$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
$^7${\small\it
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
{\small\it Via P. Giuria 1, \linebreak %
        10125 Torino, %
        Italy}\\[3mm]
        %
{\small\it
$^8$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^9$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^{10}$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]        
        }

@@

\section{Definition of the process}
\label{sec:definition}

\input{definition}

\section{Details of the calculations}
\label{sec:details}

\subsection{Several descriptions for one process}

\input{process}

@@

\section{Leading-order study}
\label{sec:LO}

\subsection{Scan}

\input{scanLO}

\subsection{Comparison in the fiducial region}

\input{crosssectionLO}

\input{distributionsLO}

\section{Next-to-leading order QCD}
\label{sec:NLO}

\subsection{ScanNLO}

\input{scanNLO}

\subsection{Comparison in the fiducial region}

\input{crosssectionNLO}

\input{distributionsNLO}

\section{Matching to parton shower}
\label{sec:matching}

@@

\section{Conclusion}
\label{sec:conclusion}

\input{conclusion}

### 2017-12-08 Draft/definition.tex
First attempt of Mathieu on draft, to be continued

\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
\end{figure}

@@

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
FIGURE
\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}
\newpage

\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}

The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
\begin{itemize}
\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
\end{itemize}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations. RIGHT SIDE FIG. IN PREPARATION. QUESTION: is RECOLA calc. 'exact' ?}\label{fig:ratio2d_NLO}
\end{figure}

>>>>

Defintion of the process. \\
Explaining the various contributions. \\
Show few Feynman diagrams and explain that it possesses also tri-boson contribuitions in the s-channel. \\

% \subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
\end{figure}

@@

### 2017-12-08 Draft/introduction.tex
First attempt of Mathieu on draft, to be continued

The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.

In the last decade many codes capable of performing VBS simulations have appeared.
Within a network such as VBSCan it is therefore natural to perform 
a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
They differ, for example
by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
The reason of these differences is that, 
when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.

>>>>

The vector-boson scattering (VBS) process with two positively charged W boson is just starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
A whole class of new processes will therefore be measured during Run~II at the Large Hadron Collider (LHC).
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematics.

The $\PW^+\PW^+$ scattering is probably the simplest VBS processes to compute and to measure due to its particular charge structure and low background, respectively.
Therefore, it is an ideal example for a detailed study of various theoretical predictions.
In the last few years, several (N)LO computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
process~\cite{Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Rauch:2016pai}.
These computations all relied on approximations while recently the complete NLO corrections became available \cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} \MP{more references?} no detailed comparison of the VBS approximations have been carried out.

The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order (LO) 
[$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$].
They are refer to as EW, interference, and QCD contributions respectively.
The EW contribution is sometimes referred to as the VBS contribution even it possesses not-VBS contributions.
Therefore, we start with a LO study of these contributions as a function of typical VBS cuts.
This allows to understand the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders 
$\mathcal{O}{\left(\alpha^{7}\right)}$,
$\mathcal{O}{\left(\alphas\alpha^{6}\right)}$,
$\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and
$\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one is the EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ \cite{Biedermann:2016yds,Biedermann:2017bss}.
The contribution of order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution.
It is often referred as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on.
It is therefore usually referred to as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.

Finally, several predictions featuring parton shower are compared.
This allows to infer systematics differences between the various predictions.
This is the first time in the literature that such an analysis has been carried out \MP{True?}.

Obviously all VBS processes deserve such a study but the present article sets the standard for inferring systematics related to NLO corrections and beyond.

The article is organised as follow:
in the first part (section~\ref{sec:definition}), the process studied is defined.
Then, various approximation at LO and NLO are described in section~\ref{sec:details}.
It is followed by a presentation of the various programs used for the simulations.
Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
Section~\ref{sec:matching} deals with the matching to parton shower.
The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations.

### 2017-12-08 Draft/scanLO.tex
First attempt of Mathieu on draft, to be continued

\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
\end{figure}

\begin{figure}[hbt]
\centering %jjpeak_diag
\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
\end{figure}

@@

\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}

>>>>

@@

% \subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
